---
title: "Alcohol vs Seat choice"
author: "Shaun ikeuchi"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
 
Data are from the UCDavis.csv
Is the average amount of alcohol consumer per week different for the different seating rows?

Null Hypothesis: There is no difference in the average amount of alcohol consumer per week based on seating row

Alternative Hypothesis: There is a difference in the average amount of alcohol consumed per week based on seating row. 

#Methods
We predict alcohol consumption based on row. 

alcohol ~ Seat
Alcohol is a numeric variable
Seat is a categorical variable.
So we use the numerical categorical variable.
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


